---
title: Data
output: 
  html_document: 
    toc: true
    toc_float: true
    number_sections: yes
    code_folding: show
---


```{r setup, include = F}
library(knitr)
knitr::opts_chunk$set(list(echo=TRUE,
                           eval=TRUE,
                           cache=FALSE,
                           warning=FALSE,
                           message=FALSE))
opts_chunk$set(fig.width = 6, fig.height = 6)
```


```{r, eval=FALSE, echo=FALSE}
dir.create("./data/")
file.copy(from="~/btsync/mk/data/sdmr/sdmr_4_english_language_versionN.csv", to="./data/")
file.copy(from="~/btsync/mk/data/sdmr//sdmr_4_english_language_versionN.RData", to="./data/")
file.copy(from="~/btsync/mk/data/sdmr/sdmr_4_english_language_versionL.csv", to="./data/")
file.copy(from="~/btsync/mk/data/sdmr//sdmr_4_english_language_versionL.RData", to="./data/")

file.copy(from="~/btsync/mk/data/sdmr/merged_4wave20151110N.csv", to="./data/")
file.copy(from="~/btsync/mk/data/sdmr/merged_4wave20151110N.RData", to="./data/")
file.copy(from="~/btsync/mk/data/sdmr/merged_4wave20151110L.csv", to="./data/")
file.copy(from="~/btsync/mk/data/sdmr/merged_4wave20151110L.RData", to="./data/")
```

# Raw data 


| What                            |.sav | .csv numeric | .csv labels | .RData numeric | .RData labels |
| ------------------------------- |---- | ------------ |------------- |--------------- |-------------- |
| sdmr_4_english_language_version | [.sav](./data/sdmr_4_english_language_version.sav) | [.csv L](./data/sdmr_4_english_language_versionL.csv) | [.csv N](./data/sdmr_4_english_language_versionN.csv) | [.Rdata N](./data/sdmr_4_english_language_versionN.RData) | [.Rdata L](./data/sdmr_4_english_language_versionL.RData) |
| merged_4wave20151110            | [.sav](./data/merged_4wave20151110.sav) | [.csv L](./data/merged_4wave20151110L.csv) | [.csv N](./data/merged_4wave20151110N.csv) | [.Rdata N](./data/merged_4wave20151110N.RData) | [.Rdata L](./data/merged_4wave20151110L.RData) |
| with class vars |  |  |   | [d_merge_N_class.RData](./data/d_merge_N_class.RData) |  [d_merge_L_class.RData](./data/d_merge_L_class.RData)   |

# Complex generic constructed variables

Variables that are theoretically sound and complex to compute and worth of including in the data!

## Year 2015

| Description                  | file     | Stata-script | SPSS-syntax  | R-script    |  
| -------------------------    | -------- | ----------   | ----------   | -------     |
| **for 2015 data**            |          |          |          |          |
| Wright class vars            | [.csv]() | [varx.do]()  | [varx.sps]() | [varx.r]()  |
| Kivinen class & autonomy     | [.csv]() | [vary.do]()  | [vary.sps]() | [class_variable1.R](./code/class_variable1.R)  |
| Something else               | [.csv]() | [varz.do]()  | [varz.sps]() | [varz.r]()  |
| **for all wawes**            |          |          |          |          |
| Wright class vars            | [.csv]() | [varx.do]()  | [varx.sps]() | [varx.r]()  |
| Kivinen class & autonomy     | [.csv]() | [vary.do]()  | [vary.sps]() | [vary.r]()  |
| Something else               | [.csv]() | [varz.do]()  | [varz.sps]() | [varz.r]()  |

# Merged data

Data with all the variables shown above!

| What                            |.sav | .csv numeric | .csv labels | .RData numeric | .RData labels |
| ------------------------------- |---- | ------------ |------------- |--------------- |-------------- |
| structure_2015_with_class       | [.sav](./data/structure_2015_with_class.sav)  | |   |   |   |
| merged_4wave   | [.sav](./data/merged_4wave.sav)    | |   |   |   |
| STR_1991a_1998_2007_2015 (Wright,etc.)-1   | [.sav](./data/STR_1991a_1998_2007_2015 (Wright,etc.)-1.sav)   | |   |   |   |
| merged_database_new_class_groups_and_autonomy_09032016   | [.sav](./data/merged_database_new_class_groups_and_autonomy_09032016.sav)   | |   |   |   |


# Using the datas

## In R

Type:

```{r loadR, eval=FALSE}
# Cross-sectional NUMERIC 2015 raw data
load(url("http://muuankarski.kapsi.fi/aisurvey/data/sdmr_4_english_language_versionN.RData"))
# Cross-sectional LABELS 2015 raw data
load(url("http://muuankarski.kapsi.fi/aisurvey/data/sdmr_4_english_language_versionL.RData"))
```



